Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-10 writing/embedded_meta_learning.tex
Further tightening

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks. Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well. Error-bars are bootstrap 95\%-CIs.}
\label{poly_continual_results}
\end{figure}
\textbf{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example of a task it has seen at each inference step. We would like to be able to store our knowledge about the tasks in a way that allows it to be more carefully refined. Furthermore, we would like the system to be able to adapt to new tasks (that it cannot perfectly solve from examples) without catastrophically interfering with our prior knowledge \citep{McCloskey1989}. \par
A very simple solution to these problems is naturally suggested by our architecture. Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step. This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task. That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[c.f.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par 
To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks. We trained on these new tasks by starting from the meta-learning network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters. The results are shown in fig. \ref{poly_continual_results}. The meta-network embeddings offers good immediate performance, and substantially accelerates the optimization the process, compared to a randomly-initialized embedding (see supp. fig. \ref{supp_poly_continual_results} for a more direct comparison). Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network. \par

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks. Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well. Error-bars are bootstrap 95\%-CIs.}
\label{poly_continual_results}
\end{figure}
\textbf{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example it has seen at each inference step. We would like to be able to store our knowledge more efficiently, and allow for further refinement. Furthermore, we would like the system to be able to adapt to new tasks (for which its guessed solution isn't perfect) without catastrophically interfering with prior tasks \citep{McCloskey1989}. \par
A very simple solution to these problems is naturally suggested by our architecture. Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step. This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task. That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[c.f.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par 
To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks. We trained on these new tasks by starting from the meta-learning network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters. The results are shown in fig. \ref{poly_continual_results}. The meta-network embeddings offers good immediate performance, and substantially accelerates the optimization the process, compared to a randomly-initialized embedding (see supp. fig. \ref{supp_poly_continual_results} for a more direct comparison). Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network. \par
